\section{Experience:}

\jobs
{Nov 2021}{}{Ongoing}
{Bioinformatics Scientist, Axle Informatics}
{I work on multiple projects at the National Institute of Allergy and Infectious Diseases (NIAID), the National Institute of Arthritis and Musculoskeletal and Skin Diseases (NIAMS), and the National Heart, Lung, and Blood Institute (NHLBI). The projects include analyzing whole genome sequencing, bulk RNA-seq, single-cell RNA-seq, proteomics , survival analysis, machine learning, and data mining. Throughout these projects, I am contributing to the study of many diseases such as AIDS, rheumatoid arthritis, capillary syndrome, cryptococcal meningitis, T-cell exhaustion, and viral infections, including COVID-19.}

\vspace{-0.6cm}

\jobs
{Sep 2021}{to}{Oct 2021}
{Bioinformatics Analyst III, Leidos Biomedical Research Inc.}
{My primary responsibility is to provide statistical genetics and bioinformatics support to the projects at the NIAID and the NIAIMS. The projects include the rare variant association of scleroderma and Systemic Capillary Leak Syndrome (SCLS) and the effect of arthritis on a patient's financial and social life.}

\vspace{-0.6cm}

\jobs
{Jan 2020}{to}{Aug 2021}
{Postdoctoral Associate, Institute for Behavioral Genetics, CU Boulder}
{In collaboration with multiple labs, I am working on uncovering genetic and phenotypic correlations among different pain conditions using UK Biobank data. In another project, I am investigating the performance of dosage data in estimating heritability compared to the hard-call genotype. I am co-supervising two graduate students in their projects on genetic genetic correlations of behavioral traits using a genetic relationship matrix-based approach and quantifying phenotypic assortment.}

\vspace{-0.6cm}

\jobs
{May 2015}{to}{Dec 2019}
{Research Assistant, Dept. of Mathematical and Statistical Science, CU Denver}
{I was involved in genetic risk prediction of generalized vitiligo. My responsibilities were data pre-processing, genome-wide association analysis, modeling polygenic risk scores, comparing multiple risk score models, dissect risk score models using functional annotation. I was also involved in analyzing secondary phenotypes and advanced method development to incorporate phenotypic heterogeneity into the association framework.}

\vspace{-0.6cm}

\jobs
{May 2018}{to}{Jul 2018}
{Collaboration with Department of Electrical Engineering, CU Denver}
{The Objective of this project was real-time electricity price forecasting to optimize electricity cost. I applied an artificial neural network on an intuitively designed feature space for forecasting electricity prices in real-time.}

\vspace{-0.6cm}

\jobs
{June 2017}{to}{July 2017}
{Research Assistant, Dept. of Mathematical and Statistical Science, CU Denver}
{A functional data analysis approach was developed to model spatiotemporal data. In this project, I used sparse matrices, numerical linear algebraic methods, and parallel computing to reduce computational expenses.}
